Topic and tone of political news articles in German online media.

### 2018-03-31 paper/docs/04_Modelresults_50.Rmd
add wordclouds

The Figures below show the distribution of the number of articles from the respective news sources by date. There is a high peak around the federal elections on September, 24th.

@@

![plot1](../figs/bar.png)
```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  group_by(date) %>%
  dplyr::summarise(obs = n()) %>%
  ggplot(aes(date, obs)) +
  geom_line(color=col[3]) +
  geom_vline(aes(xintercept=as.Date("2017-09-24")),
             linetype = 2, color=col[5]) +
  scale_color_manual(values = col) +
  labs(x="", y="number of articles",color="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(
      legend.position   = "none",
      axis.title.x      = element_blank(),
      axis.text       = element_text(size = 8)
    )
},
filename = "../figs/timeline.png", device = "png",width = 6, height = 4,
dpi = 600
)

@@

@@

ggsave(plot = {
  btw %>%
    ggplot(aes(as.numeric(text_length.cut),
                       group = site)) +
    geom_histogram(aes(y=..density..), alpha=.8, fill = col[3]) + 
    scale_x_continuous(labels = c(seq(0,1500,500), ">2000")) +
    facet_wrap(~site, ncol = 4) +
    labs(x = "Word count", color = "") +
    theme(axis.title = element_text(size = 8),
          axis.text = element_text(size = 6))

@@

To summarise the content of the texts, wordclouds help to get a first impression, as they represent the number of words in a corpus. Intuitively the term frequency (tf) of a word is a measure of how important that word may be. The following word cloud is derived from the whole corpus. As can be seen, problems arise with high frequency words. For example "die", "der", and "in" are extremly common but unrelated to the quantity of interest. These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected.  We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized list of stop-words that are redundant superfluous or distorting. We also remove punctuation character (e.g. ., ,, !, ?, etc.) and all numbers from our corpus.

@@

After completing this steps we were left with 68.576 unique terms in our vocabulary. The following wordclouds is derived from the corpus for each news provider. It becomes evident that these are texts discussing domestic policy issues. The SPD in particular seems to be higly frequent. However, at first glance, there are no obvious differences between the corpus of the different news provider.

>>>>

The Figures below show the distribution of the number of articles from the respective news sources by date. There is a high peak around the federal elections on September, 24th and another one shortly after the failure of the Jamaica coalition talks on November, 19th (indicated by the red dotted lines). The Figure on the right shows, that DIE WELT published most articles on domestic policy, followed by stern.de and FOCUS ONLINE.

@@

![plot1](../figs/bar.png)
```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  group_by(date) %>%
  dplyr::summarise(obs = n()) %>%
  ggplot(aes(date, obs)) +
  geom_line(color=col[3]) +
  geom_vline(aes(xintercept=as.Date("2017-09-24")),
             linetype = 2, color=col[5]) +
  geom_vline(aes(xintercept=as.Date("2017-11-19")),
             linetype = 2, color=col[5]) +
  scale_color_manual(values = col) +
  labs(x="", y="number of articles",color="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(
      legend.position   = "none",
      axis.title.x      = element_blank(),
      axis.text       = element_text(size = 8)
    )
},
filename = "../figs/timeline.png", device = "png",width = 6, height = 4,
dpi = 600
)

@@

Most of the articles have a word length between 200 and 1000 words (articles with less than 200 words were filtered out in advance, as these are mostly reader comments). The distribution at Bild.de, DIE WELT, FOCUS ONLINE and stern.de is left-skewed, whereby stern.de has comparatively many articles with a word length of over 2000.

The longest article at Tagesschau.de has 2006 words, nevertheless the median value is comparatively large (see the Table below). ZEIT ONLINE has the highest median value of 459 words.

@@

ggsave(plot = {
  btw %>%
    ggplot(aes(as.numeric(text_length.cut),
                       group = site)) +
    geom_histogram(alpha=.8, fill = col[3]) + 
    scale_x_continuous(labels = c(seq(0,1500,500), ">2000")) +
    facet_wrap(~site, ncol = 4) +
    labs(x = "Word count", color = "") +
    theme(axis.title = element_text(size = 8),
          axis.text = element_text(size = 6))

@@

To summarise the content of the texts, wordclouds help to get a first impression, as they represent the number of words in a corpus. Intuitively the term frequency (tf) of a word is a measure of how important that word may be. The following word cloud is derived from the whole corpus. As can be seen, problems arise with high frequency words. For example "die", "der", and "in" are extremely common but unrelated to the quantity of interest. These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected.  We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized list of stop-words that are redundant or distorting. We also remove punctuation character (e.g. ., ,, !, ?, etc.) and all numbers from our corpus.

@@

After completing this steps we were left with 68.576 unique terms in our vocabulary. The following wordclouds are derived from the corpus for each news provider. It becomes evident that these are texts discussing domestic policy issues. The SPD in particular seems to be higly frequent. However, at first glance, there are no obvious differences between the corpus of the different news provider.

### 2018-03-31 paper/writing/structure.tex
add wordclouds

\documentclass[12pt,a4paper,notitlepage]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[backend=biber,
			style=authoryear-comp,
			isbn=false,
			doi=false,
			bibstyle=authoryear,
			natbib,
			]{biblatex}
\usepackage{eurosym}
\usepackage{enumitem}
\usepackage{url}
\usepackage{blindtext}
\usepackage{hyperref}
\usepackage{breakurl}
\usepackage{amsmath}
\usepackage{titling}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{pgfplots}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{tikz-3dplot}
\usepackage{subcaption}
\usepackage{float}
\usepackage{adjustbox}
\usepackage{multirow,rotating}
\usepackage[autostyle]{csquotes}
\usepackage[toc,page]{appendix}
\usepackage{lscape}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{bm}
\usepackage{eurosym}
\usepackage{pdflscape}

@@

I conduct the estimation on a sample of 14,937 online news articles from seven german news provider about domestic politics\footnote{Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, stern.de, ZEIT ONLINE, Tagesschau.de}. The articles are dated from 01.06.2017 to 01.03.2018. I first extract all online articles using the the Webhose.io API.\footnote{For more information see https://docs.webhose.io/v1.0/docs/getting-started. The scraping code was written in Python and can be made available on request.} Then all articles from the section "domestic policy" are filtered by using the URL of an article. Figure \ref{fig_distr1} shows the distribution of the number of articles from the respective news sources by date. There is a high peak around the federal elections on September, 24th.

@@

Overall, the selected news providers are among the top ten German online news providers in the period under review, with only Tagesschau.de belonging to the public media. The reason for this is that the content structure of Tagesschau.de is most similar to that of the private providers. ZDF.de offers predominantly video content and DLF website mainly offers audio content in the form of interviews, which makes it hard to include it in the model.

% ------------------
% Text Pre-Procesing
% ------------------
% Mehr beschreiben was hier gemacht wird. Was ist z.b. eine stop-word list?

A central task in text mining is to extract low-dimensional information from documents that are high-dimensional by nature \citep{bholat_text_2015}. This is related to the task of reducing the number of unique language elements in order to reduce the dimensionality of data (to avoid unnecessary computational complexity and overfitting) while at the same time keeping those words that reflect the content of a document. Any useful representation of text will throw away some information, the trick is to include the relevant information that is needed, and exclude the extraneous information. A common strategy to use text as data and reduce the dimensionality, is to pre-process the text by imposing some preliminary restrictions (stop-word removal, tokenization) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) to reduce the number of language elements \citep{gentzkow_text_2017}.

Intuitively the term frequency (tf) of a word is a measure of how important that word may be. There are words in a document, however, that occur many times but may not be important like articles, conjunctions, and so on. These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected. We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized list of stop-words that are redundant superfluous or distorting. We also remove punctuation character (e.g. ., ,, !, ?, etc.) and all numbers from our corpus. After completing this steps we were left with 68.576 unique terms in our vocabulary.

After pre-processing, each document $d$ is a finite list of terms. Each unique term in the corpus is indexed by some $v \in \lbrace 1,...,V \rbrace$ where $V$ is the number of unique terms. For each document $d \in \lbrace 1,...,D \rbrace$ we compute the number of occurrences of term $v$ in document $d$ to obtain the count $x_{d,v}$. The $D$ x $V$ matrix $\boldsymbol{X}$ of all such counts is called the document-term matrix. This representation is often referred to as the bag of words model, since the order in which words are used within a document is completely disregarded.

% ----------------------
% Structural topic Model
% ----------------------
\section{The structural topic model}\label{ch_model}
% Kapitel mehr mit eigenen Worten beschreiben.

The structural topic model (STM) developed by \citet{roberts_model_2016} allows to incorporate document specific covariates (e.g. the author or date of a document). STM is a recent extension of the standard topic modeling technique, labeled as "latent Dirichlet allocation" (LDA), which refers to the Bayesian model in \citet{blei_latent_2003} that treats each word in a topic and each topic in a document as generated from a Dirichlet - distributed prior.\footnote{See also \citet{griffiths_probabilistic_2002}, \citet{griffiths_finding_2004} and \citet{hofmann_probabilistic_1999}. \citet{pritchard_inference_2000} introduced the same model in genetics for factorizing gene expression as a function of latent populations.} Topic models formalize the idea that documents are formed by hidden variables (topics) that generate correlations among observed terms. Since its introduction into text analysis, LDA has become hugely popular and especially useful in political science.\footnote{see \citet{blei_probabilistic_2012}, \citet{grimmer_text_2013} and \citet{wiedmann_text_2016} for an overview in social science and \citet{gentzkow_text_2017} give an overview of text mining applications in economics.} \citet{wiedmann_text_2016} uses topic model methods on large amounts of news articles from two german newspapers published between 1959 and 2011, to reveal how democratic demarcation was performed in Germany over the past six decades. \citet{paul_cross-collection_2017} compares editorial differences between media sources, using cross-collection latent Dirichlet allocation (ccLDA), an LDA-based approach that incorporates differences in document metadata. They use a dataset of 623 news articles from August 2008 from two American media outlets - msnbc.com and foxnews.com - to compare how they discuss topics. Reviewing the top words of the word-topic distribution, they find some content differences between the two.

STM has been applied to multiple academic fields: \citet{roberts_structural_2014} uses STM to analyze open-ended responses from surveys and experiments, \citet{farrell_corporate_2016} applies the model to scientific texts on climate change, revealing links between corporate funding and the framing of scientific studies. \citet{mishler_using_2015} show that "STM can be used to detect significant events such as the downing of Malaysia Air Flight 17" when applied to twitter data. Another study shows how STM can be used to explore the main international development topics of countries’ annual statements in the UN General Debate and examine the country-specific drivers of international development rhetoric \citep{baturo_what_2017}. \citet{mueller_reading_2016} use newspaper text to predict armed conflicts in different regions. They use the estimated topic shares in linear fixed effects regression to forecast conflict out-of-sample. \citet{roberts_navigating_2016} use STM to examine the role of partisanship in topical coverage using a corpus of 13,246 posts that were written for 6 political blogs during the course of the 2008 U.S. presidential election. With the aim of revealing the effect of partisan membership on topic prevalence, each blog is assigned to be either liberal or conservative. To explore the differences between the two, they look at the expected proportion of topic and examine the posts most associated with a respective topic. This approach is similar to \citet{roberts_model_2016}. They also use different measures of distance between the topic-word distributions of the same topic within different models.

@@

As mentioned above, the STM allows to incorporate observed document metadata which is able to affect both topical prevalence and topical content. The following description of the generative model - the process of filling a word-position in a document - of the STM is based on \citet{roberts_structural_2013} and \citet{roberts_stm:_2016}. For each document $d$ and a given number of topics $K$, a document-specific topic-prevalence vector $d(\boldsymbol{\theta}_d)$ is drawn from a logistic-normal distribution, where the parameters are a function of the covariate values:

\begin{equation}
	\boldsymbol{\theta}_d|\boldsymbol{x}_{d\gamma},\boldsymbol{\Sigma} \sim \textrm{LogisticNormal}(\mu = \boldsymbol{x}_{d\gamma}\boldsymbol{\Sigma}).
\end{equation}

$\boldsymbol{x}_d\gamma$ lists the values of all metadata covariates for document $d$, where $\gamma$ relates these covariate values to the topic-prevalence. The structure of $\boldsymbol{\Sigma}$ implies the possibility of correlations across documents in the topic-prevalence vector.

According to $\theta$, a specific topic $z_{dn}$ is assigned for the $n^{th}$ word-position in the document through the process:

\begin{equation}
	z_{dn}|\boldsymbol{\theta}_d \sim \textrm{Multinomial}(\boldsymbol{\theta}_d).
\end{equation}

Conditional in the topic chosen, a specific word, $w_{dn}$, is chosen from the overall corpus vocabulary $V$, using the following process:

@@

where the word probability $\beta_{dkv}$ is parameterized in terms of log-transformed rate deviations from the rates of a corpus-wide background distribution $m_v$. The log-transformed rate deviations can then be specified by a collection of parameters $\lbrace \boldsymbol{\kappa} \rbrace$, where $\kappa^{(t)}$ is a $K$-by-$V$ matrix containing the log-transformed rate deviations for each topic $k$ and term $v$, over the baseline log-transformed rate for term $v$. This matrix is the same for all $A$ levels of covariates. To put it differently, $\kappa^{(t)}$ indicates the importance of the term $v$ given topic $k$ regardless of the covariates. Similarly, $\kappa^{(c)}$ is a $A$-by-$V$ matrix, indicating the importance of the term $v$ given the covariate level $c$ regardless of the topic. Finally, $\kappa^{(i)}$ is a $A$-by-$K$-by-$V$ matrix, collecting the covariate-topic effects:

@@

The STM maximizes the posterior likelihood that the observed data were generated by the above data-generating process using an iterative approximation-based variational expectation-maximization algorithm\footnote{A technical description of this maximization process can be found in \citet{roberts_model_2016}} available in R's stm package \citep{roberts_stm:_2016}. The process gives us two posterior distribution parameter: (1) $\beta$ is a $K$-by-$V$ matrix (where $K=$ number of topics and $V=$ vocabulary), where the entry $\beta_{kvc}$ can be interpreted as the probability of observing the $v$-th word in topic $k$ for the covariate level $c$. (2) $\theta$ is a $D$-by-$V$ matrix of the document-topic distributions, where the entry $\theta_{dk}$ can be interpreted as the proportion of words in document $d$ which arise from topic $k$, or rather as the probability that document $d$ deals about topic $k$. These probability distributions are used to compare the content of public and private news providers in section \ref{ch_empirical}.

@@

Inference of mixed-membership models, such as the one applied in this paper, has been a thread of research in applied statistics in the past few years \citep{blei_latent_2003} \citep{erosheva_mixed-membership_2004} \citep{braun_variational_2010}. Topic models are usually imprecise as the function to be optimized has multiple modes, such that the model results can be sensitive to the starting values. Since an ex ante valuation of a model is hardly possible, I compute a variety of different models and compare their posterior probability. This enables me to check how results vary for different model solution \citep{roberts_navigating_2016}. I then cross-checked some subset of assigned topic distributions to evaluate whether the estimates align with the concept of interest \citep{gentzkow_text_2017}. These manual audits are applied together with numeric optimization based on the topic coherence measure suggested by \citet{mimno_optimizing_2011}.

>>>>

\documentclass[12pt,a4paper,notitlepage]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[backend=biber,
			style=authoryear-comp,
			isbn=false,
			doi=false,
			bibstyle=authoryear,
			natbib,
			]{biblatex}
\usepackage{eurosym}
\usepackage{enumitem}
\usepackage{url}
\usepackage{blindtext}
\usepackage{hyperref}
\usepackage{breakurl}
\usepackage{amsmath}
\usepackage{titling}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{pgfplots}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{tikz-3dplot}
\usepackage{subcaption}
\usepackage{float}
\usepackage{adjustbox}
\usepackage{multirow,rotating}
\usepackage[autostyle]{csquotes}
\usepackage[toc,page]{appendix}
\usepackage{lscape}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{bm}
\usepackage{eurosym}
\usepackage{pdflscape}
\usepackage{geometry}
\geometry{a4paper,left=40mm,right=30mm, top=1cm, bottom=2cm}

@@

I conduct the estimation on a sample of 14,937 online news articles from seven german news provider about domestic politics\footnote{Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, stern.de, ZEIT ONLINE, Tagesschau.de}.  The articles are dated from 01.06.2017 to 01.03.2018. I first extract all online articles using the the Webhose.io API.\footnote{For more information see https://docs.webhose.io/v1.0/docs/getting-started. The scraping code was written in Python and can be made available on request.} Then all articles from the section "domestic policy" are filtered by using the URL of an article. Overall, the selected news providers are among the top ten German online news providers - in terms of unique user\footnote{The term unique user refers to a number of different visitors to a website within a certain period of time. Multiple visits from the same user are only considered once.} - in the period under review, with only Tagesschau.de belonging to the public media. The reason for this is that the content structure of Tagesschau.de is most similar to that of the private providers. ZDF.de offers predominantly video content and DLF (Deutschlandfunk) website mainly offers audio content in the form of interviews, which makes it hard to include it in the model.

 Figure \ref{fig_distr1} shows the distribution of the number of articles from the respective news sources by date.  There is a high peak around the federal elections on September, 24th and another one shortly after the failure of the Jamaica coalition talks on November, 19th (indicated by the red dotted lines). Figure \ref{fig_distr2} shows, that DIE WELT published most articles on domestic policy, followed by stern.de and FOCUS ONLINE.

@@

Looking at the histograms of the word counts (Figure \ref{fig_wordcount}), it becomes evident that most of the articles have a word length between 200 and 1000 words (articles with less than 200 words were filtered out in advance, as these are mostly reader comments). The distribution at Bild.de, DIE WELT, FOCUS ONLINE and stern.de is left-skewed, whereby stern.de has comparatively many articles with a word length of over 2000.

\begin{figure}[H]
	\caption{Word Count}
	\begin{center}
		\includegraphics[width=\textwidth]{../figs/wordcount.png}
		\caption{Word counts}
		\label{fig_wordcount}
	\end{center}
\end{figure}

The longest article at Tagesschau.de has 2006 words, nevertheless the median value is comparatively large (see the Table below). ZEIT ONLINE has the highest median value of 459 words.

\include{tables/wordcount}

To summarize the content of the texts, wordclouds help to get a first impression, as the frequency of words in a corpus are represented by their size. Intuitively the term frequency (tf) of a word is a measure of how important that word may be. The word cloud in Figure \ref{fig_wordcloud1} is derived from all articles within the dataset. As can be seen, problems arise with words that are highly frequent. For example "die", "der", and "in" are extremely common but unrelated to the quantity of interest. These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected. A common strategy to reduce the number of language elements is to pre-process the text by imposing some preliminary restrictions (stop-word removal and stemming) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) \citep{gentzkow_text_2017}. In fact, to use text as data and reduce the dimensionality to avoid unnecessary computational complexity and overfitting, pre-processsing the text is a central task in text mining \citep{bholat_text_2015}.

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=\textwidth]{../figs/wordcloud.png}
		\caption{Word Cloud (whole corpus)}
		\label{fig_wordcloud1}
	\end{center}
\end{figure}

Stemming is a process by which different morphological variants of a word are traced back to their common root. For example, ‘voting’ and ‘vote’ would be treated as two instances of the same token after the stemming process. There are many different techniques for the stemming process. I use the widely used Porter-Stemmer algorithm, which is based on a set of shortening rules that are applied to a word until it has a minimum number of syllables.\footnote{https://tartarus.org/martin/PorterStemmer/} To remove distorting words, the pre-defined stop word list from the Snowball project\footnote{http://snowball.tartarus.org/algorithms/german/stop.txt} together with a customized list of stop-words is used. Additionally punctuation character (e.g. ., ,, !, ?, etc.) and all numbers are removed from our corpus. After completing this steps we were left with 68.576 unique terms in our vocabulary. The following wordclouds are derived from the corpus for each news provider. It becomes evident that these are texts discussing domestic policy issues. The SPD in particular seems to be highly frequent. However, at first glance, there are no obvious differences between the corpus of the different news provider.

\begin{figure}[H]
	\caption{Word Clouds}
	\begin{center}
		\begin{subfigure}[normla]{0.3\textwidth}
			\includegraphics[width=\textwidth]{../figs/wordcloud_Bild.png}
			\caption{Bild.de}
		\end{subfigure}
		\begin{subfigure}[normla]{0.3\textwidth}
			\includegraphics[width=\textwidth]{../figs/wordcloud_DIEWELT.png}
			\caption{DIE WELT}
		\end{subfigure}
		\begin{subfigure}[normla]{0.3\textwidth}
			\includegraphics[width=\textwidth]{../figs/wordcloud_FOCUSONLINE.png}
			\caption{FOCUS ONLINE}
		\end{subfigure}
		\begin{subfigure}[normla]{0.3\textwidth}
			\includegraphics[width=\textwidth]{../figs/wordcloud_SPIEGELONLINE.png}
			\caption{SPIEGEL ONLINE}
		\end{subfigure}
		\begin{subfigure}[normla]{0.3\textwidth}
			\includegraphics[width=\textwidth]{../figs/wordcloud_stern.png}
			\caption{Stern.de}
		\end{subfigure}
		\begin{subfigure}[normla]{0.3\textwidth}
			\includegraphics[width=\textwidth]{../figs/wordcloud_Tagesschau.png}
			\caption{Tagesschau.de}
		\end{subfigure}
		\begin{subfigure}[normla]{0.3\textwidth}
			\includegraphics[width=\textwidth]{../figs/wordcloud_ZEITONLINE.png}
			\caption{ZEIT ONLINE}
		\end{subfigure}
	\end{center}
\end{figure}

% --------------------
% Document-term-matrix
% --------------------
To use the data for statistical analysis, the next step is to divide the whole corpus into individual documents and to represent these documents as a finite list of unique terms. In this setting, each news article represents a document $d$, whereby each of these documents can be assigned to a news website. Next, for each document $d \in \lbrace 1,...,D \rbrace$ the number of occurrences of term $v$ in document $d$ is computed, to obtain the count $x_{d,v}$.\footnote{Each unique term in the corpus is indexed by some $v \in \lbrace 1,...,V \rbrace$ where $V$ is the number of unique terms.} The $D$ x $V$ matrix $\boldsymbol{X}$ of all such counts is called the document-term matrix. This representation is often referred to as the bag of words model, since the order in which words are used within a document is disregarded. The sum of all documents forms what is called the corpus. 
% ----------------------
% Structural topic Model
% ----------------------
\section{The structural topic model}\label{ch_model}
% Kapitel mehr mit eigenen Worten beschreiben.

To find out the latent structure of each document, a Structural topic model (STM) is estimated. In general, topic models formalize the idea that documents are formed by hidden variables (topics) that generate correlations among observed terms. They belong to the group of unsupervised generative models, meaning that the true attributes (topics) cannot be observed. One crucial assumption to be made for such models is the number of topics that occur over the entire corpus ($K$). Each individual topic potentially contains all of the unique terms within the vocabulary $V$ with different probability. Therefore, each topic $k$ can be represented as a probability vector $\beta_k$ over all unique terms $V$. Simultaneously, each individual document $d$ in the corpus can be represented as a probability distribution $\theta_d$ over the $K$ topics. To generate each individual word $w_{d,n}$ in a document $d$ for the $n^{th}$ word-position, (1) a topic allocation $z_{d,n}$ is drawn from the topic distribution for that document $\theta_d$. (2) Then, a word is drawn from the term distribution for the selected topic $\beta_{z_{d,n}}$.

The STM developed by \citet{roberts_model_2016} is a recent extension of the standard topic modeling technique, labeled as "latent Dirichlet allocation" (LDA), which refers to the Bayesian model in \citet{blei_latent_2003} that treats each word in a topic and each topic in a document as generated from a Dirichlet - distributed prior.\footnote{See also \citet{griffiths_probabilistic_2002}, \citet{griffiths_finding_2004} and \citet{hofmann_probabilistic_1999}. \citet{pritchard_inference_2000} introduced the same model in genetics for factorizing gene expression as a function of latent populations.} Since its introduction into text analysis, LDA has become hugely popular and especially useful in political science.\footnote{see \citet{blei_probabilistic_2012}, \citet{grimmer_text_2013} and \citet{wiedmann_text_2016} for an overview in social science and \citet{gentzkow_text_2017} give an overview of text mining applications in economics.} \citet{wiedmann_text_2016} uses topic model methods on large amounts of news articles from two german newspapers published between 1959 and 2011, to reveal how democratic demarcation was performed in Germany over the past six decades. \citet{paul_cross-collection_2017} compares editorial differences between media sources, using cross-collection latent Dirichlet allocation (ccLDA), an LDA-based approach that incorporates differences in document metadata. They use a dataset of 623 news articles from August 2008 from two American media outlets - msnbc.com and foxnews.com - to compare how they discuss topics. Reviewing the top words of the word-topic distribution, they find some content differences between the two.

The STM allows to incorporate document specific covariates (e.g. the author or date of a document). The model has been applied to multiple academic fields: \citet{roberts_structural_2014} uses STM to analyze open-ended responses from surveys and experiments, \citet{farrell_corporate_2016} applies the model to scientific texts on climate change, revealing links between corporate funding and the framing of scientific studies. \citet{mishler_using_2015} show that "STM can be used to detect significant events such as the downing of Malaysia Air Flight 17" when applied to twitter data. Another study shows how STM can be used to explore the main international development topics of countries’ annual statements in the UN General Debate and examine the country-specific drivers of international development rhetoric \citep{baturo_what_2017}. \citet{mueller_reading_2016} use newspaper text to predict armed conflicts in different regions. They use the estimated topic shares in linear fixed effects regression to forecast conflict out-of-sample. \citet{roberts_navigating_2016} use STM to examine the role of partisanship in topical coverage using a corpus of 13,246 posts that were written for 6 political blogs during the course of the 2008 U.S. presidential election. With the aim of revealing the effect of partisan membership on topic prevalence, each blog is assigned to be either liberal or conservative. To explore the differences between the two, they look at the expected proportion of topic and examine the posts most associated with a respective topic. This approach is similar to \citet{roberts_model_2016}. They also use different measures of distance between the topic-word distributions of the same topic within different models.

@@

 As mentioned above, the STM allows to incorporate observed document metadata which is able to affect both topical prevalence and topical content. These assumptions are reflected in the prior distributions. The following describes the generative process for filling the $n^{th}$ word-position in document $d$ in the case of the STM \citep{roberts_structural_2013}: As in the case of conventional models, (1) a specific topic $z_{dn}$ is assigned, according to the topic distribution for that document $\theta$ through the process:

\begin{equation}
	z_{dn}|\theta_d \sim \textrm{Multinomial}(\theta_d).
\end{equation}

To incorporate the covariate values for that document, a topic-prevalence vector $\theta_d$ is drawn from a logistic-normal distribution:

\begin{equation}
	\theta_d|x_{d\gamma},\Sigma \sim \textrm{LogisticNormal}(\mu = x_{d\gamma}\Sigma),
\end{equation}

where $x_d\gamma$ lists the values of all metadata covariates for document $d$, where $\gamma$ relates these covariate values to the topic-prevalence. The structure of $\Sigma$ implies the possibility of correlations across documents in the topic-prevalence vector.

Then again, (2) conditional in the topic chosen ($z_{dn}$), a specific word $w_{dn}$, is chosen from the overall corpus vocabulary $V$, using the following process:

@@

where the word probability $\beta_{dkv}$ is parameterized in terms of log-transformed rate deviations from the rates of a corpus-wide background distribution $m_v$ \citep{roberts_structural_2013}. The log-transformed rate deviations can then be specified by a collection of parameters $\lbrace \boldsymbol{\kappa} \rbrace$, where $\kappa^{(t)}$ is a $K$-by-$V$ matrix containing the log-transformed rate deviations for each topic $k$ and term $v$, over the baseline log-transformed rate for term $v$. This matrix is the same for all $A$ levels of covariates. To put it differently, $\kappa^{(t)}$ indicates the importance of the term $v$ given topic $k$ regardless of the covariates. Similarly, $\kappa^{(c)}$ is a $A$-by-$V$ matrix, indicating the importance of the term $v$ given the covariate level $c$ regardless of the topic. Finally, $\kappa^{(i)}$ is a $A$-by-$K$-by-$V$ matrix, collecting the covariate-topic effects:

@@

The STM maximizes the posterior likelihood that the observed data were generated by the above data-generating process using an iterative approximation-based variational expectation-maximization algorithm\footnote{A technical description of this maximization process can be found in \citet{roberts_model_2016}} available in R's stm package \citep{roberts_stm:_2016}.

This process generates two posterior distribution parameter: (1) $\beta$ is a $K$-by-$V$ matrix (where $K=$ number of topics and $V=$ vocabulary), where the entry $\beta_{kvc}$ can be interpreted as the probability of observing the $v$-th word in topic $k$ for the covariate level $c$. (2) $\theta$ is a $D$-by-$V$ matrix of the document-topic distributions, where the entry $\theta_{dk}$ can be interpreted as the proportion of words in document $d$ which arise from topic $k$, or rather as the probability that document $d$ deals about topic $k$. These probability distributions are used to compare the content of the different news provider in section \ref{ch_empirical}.

@@

Inference of mixed-membership models, such as the one applied in this paper, has been a thread of research in applied statistics in the past few years \citep{blei_latent_2003} \citep{erosheva_mixed-membership_2004} \citep{braun_variational_2010}. Topic models are usually imprecise as the function to be optimized has multiple modes, such that the model results can be sensitive to the starting values (e.g. the number of topics). Since an ex ante valuation of a model is hardly possible, I compute a variety of different models and compare their posterior probability. This enables me to check how results vary for different model solution \citep{roberts_navigating_2016}. I then cross-checked some subset of assigned topic distributions to evaluate whether the estimates align with the concept of interest \citep{gentzkow_text_2017}. These manual audits are applied together with numeric optimization based on the topic coherence measure suggested by \citet{mimno_optimizing_2011}.
